### 2016-01-09 pdocs/thesis/discussion.tex
pdocs

\subsubsection{Large displacements}

\subsubsection{Material nonlinearity}

>>>>

\subsubsection{Acceptance to current physics engines}

Required work depends on selected dynamics engine. Availability of these features makes similar 
implementation possible.

\begin{itemize}
\item generic spring or motor constraint is already available 
\item possibility to update constraints after each simulation step
\end{itemize}

Current implementation is done based on \bullet but it still needs refactoring and testing before it can be 
accepted to main stream. Interfaces should be reafctored so that handling of additional features like large 
displacements and material nonlinearity can be implemented without further changes.

\subsubsection{Large displacements}
Large displacements are typical if plasticity is involved and
large displacements can also take place due to rigid body motion and should be taken into account.

Update of constraints can be done in  many ways but using callbacks allows clean integration i.e. no changes
to solver core are needed.
In \bullet there are already three per step callbacks.

\begin{itemize}
\item updateActions
\item updateActivationState
\item btInternalTickCallback
\end{itemize}

\demolisher already uses updateActions and that seems 
good way to do also other updates. Special care should be taken to avoid unnecessary updates.

\subsubsection{Material nonlinearity}
Update of constraint properties can be done in callbacks in similar way as for large displacements.
Material definition should be defined so that stress-strain curve can be defined as array of pairs.

### 2016-01-09 pdocs/thesis/introduction.tex
pdocs

\subsection{Physics engines}

@@

@@

Physics engines are not commonly used in structural analysis but using structural analysis in physics engines is not rare.

E.g. \cite{Obrien:1999:GMA} used finite element model to analyze crack initiation and propagation.

@@

This work opens wide area of further work of combining structural analysis and plasticity with physics engines.
Few examples are shown in sections~\ref{sec:results} and possible areas of further work are discussed in \ref{subsec:futureWork}.

>>>>

Figure \ref{fig:areas} summarizes branches involved in this work.

\begin{figure}[htb!]
\centering
\begin{tikzpicture}
  \begin{scope}[blend group = soft light]
    \fill[red!30!white]   ( 90:3.2) circle (5);
    \fill[green!30!white] (210:3.2) circle (5);
    \fill[blue!30!white]  (330:3.2) circle (5);
  \end{scope}
  \node at ( 90:5)   [align=left] {solid mechanics\\
structural analysis\\
material plasticity};
  \node at ( 210:4)   [align=left] {mechanics\\
physics engine\\
rigid bodies\\
constraints};
  \node at ( 330:5.5)   [align=left] {computer sciences\\
software engineering\\
extending of bulletphysics\\
verification
};
  \node {\begin{varwidth}{2cm}handling of plasticity in physics\\
engine\end{varwidth}};
\end{tikzpicture}
\caption{Multidisciplinary approach to plasticity in physics engine.}
\label{fig:areas}
\end{figure}

In this work all theories in area of structural analysis are quite old and e.g. 
\cite{timoshenko} is typical reference. Main focus is on elastic and 
linear plastic parts of stress-strain curve and elastic and plastic section modulus.

\begin{figure}[htb!]
\centering
\begin{tikzpicture}
\draw[->] (0,0) -- (10,0) node[right] {\large{$\epsilon$}};
\draw[->] (0,0) -- (0,8) node[above] {\large{$\sigma$}};
\draw(0,0) -- (2,4) -- (4,4) .. controls (7,6) .. (10,5);
\draw[dashed](0,4) -- (2,4);
\node at (-0.2,4) [align=right] {$f_y$};
\end{tikzpicture}
\caption{Stress-strain curve of ductile steel (not to scale).}
\label{fig:areas}
\end{figure}

\subsection{Physics engine}

@@

Physics engines cannot used in serious structural analysis but using structural analysis in physics engines is not rare.  
E.g. \cite{Obrien:1999:GMA} used finite element model to analyze crack initiation and propagation.

@@

\subsection{software engineering}

@@

This work opens wide area of further work of combining structural analysis and plasticity with physics engines.
Few examples are shown in sections~\ref{sec:results} and possible areas of further work are discussed in section \ref{subsec:futureWork}.
